Excel fun

### 2022-07-11 Excel fun.Rmd
Filtering and summarising.

```{r}
test2 <- test |> 
  mutate(
    category = ifelse(is.na(value), entry, NA)
  ) |> 
  fill(category) |> 
  fill(year) |> 
  filter(!is.na(value))
test2
```

>>>>

```{r}
test2 <- test |> 
  mutate(
    category = ifelse(is.na(value), entry, NA)
  ) |> 
  fill(category) |> 
  fill(year) |> 
  filter(!is.na(value))
test2 |> 
  filter()

test2_no_totals <- test2 |> 
  filter(
    !str_detect(entry, "^Sum") & !str_detect(entry, "^Total")
  )

test2_no_totals
test2_no_totals |>
  group_by(category) |> 
  summarise(
    sum = sum(value)
  )
```
